VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-18 snapshot_system/paper_analysis.tex
revise for ACM cloud
remove mbox

\subsection{Fault Isolation}

@@

For VO, 
%each VM has an average of $N_o$ file system blocks
%and let $V_o$ be the average number of VMs shared by each file block.
by counting outgoing edges from VMs in Figure~\ref{fig:share}(b) with parameters defined in
Table~\ref{tab:symbol},  we have
$
n *N_o   =  V_o *\mbox{ Number of file system blocks in VO.} 
$

>>>>

\section{Impact on Fault Isolation}

@@

For VO, 
%each VM has an average of $N_o$ file system blocks
%and let $V_o$ be the average number of VMs shared by each file block.
by counting outgoing edges from VMs in Figure~\ref{fig:share}(b) with parameters defined in
Table~\ref{tab:symbol},  we have $n *N_o   =  V_o * $Number of file system blocks in VO.
